**PRACTICAL 1**

**Question 1**

The rows in the air quality data set that do not have values are:

```{r}
data <- airquality
index <- c(which(is.na(data$Ozone)),which(is.na(data$Solar.R)),which(is.na(data$Wind)),which(is.na(data$Temp)),which(is.na(data$Month)),which(is.na(data$Day)))
index <- sort(unique(index))
index
```

**Question 2**

The mean and standard deviation respectively for temperature in the air quality data set are:

```{r}
mean(data$Temp)
sd(data$Temp)
```

The maximum and minimum respectively for temperature in the air quality data set are:

```{r}
max(data$Temp)
min(data$Temp)
```

The mean and standard deviation respectively for ozone in the air quality data set are:

```{r}
mean(data$Ozone,na.rm = TRUE)
sd(data$Ozone, na.rm = TRUE)
```

The maximum and minimum respectively for ozone in the air quality data set are:

```{r}
max(data$Ozone, na.rm = TRUE)
min(data$Ozone, na.rm = TRUE)
```

**Question 3**

```{r}
data_car <- cars
Y <- data_car$dist
X <- matrix(1,nrow=50,ncol=2)
X <- cbind(1,data_car$speed)
XT <- t(X)
XTX <- XT %*% X
inverse <- solve(XTX)
solution <- inverse %*% XT %*% Y
solution
```

```{r}
lm(data_car$dist~data_car$speed)
```
